---
title: "Gun Violence By 115th Congressional Districts"
output: 
  html_document:
    css: style.css
    includes:
      in_header: header.html
      after_body: footer.html
      
---
<style> .main-container {max-width:100%; padding:0;} </style>

<svg aria-hidden="true" focusable="false" style="width:0;height:0;position:absolute;">
<linearGradient id="gradient-across" x2="1" y2="1">
<stop offset="0%" stop-color="var(--color-stop-1)" />
<stop offset="50%" stop-color="var(--color-stop-2)" />
<stop offset="100%" stop-color="var(--color-stop-3)" />
</linearGradient>
</svg>

<svg aria-hidden="true" focusable="false" style="width:0;height:0;position:absolute;">
<linearGradient id="gradient-across-2" y2="1">
<stop offset="0%" stop-color="var(--color-stop-1)" />
<stop offset="50%" stop-color="var(--color-stop-2)" />
<stop offset="100%" stop-color="var(--color-stop-3)" />
</linearGradient>
</svg>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(leaflet)
library(maps)
library(RColorBrewer)
library(sf)
# district gini index
Census_CD115_Gini_Index_17_5YR <- read_csv("C:/Users/ignac/Desktop/RRepository/GunViolenceArchive/Data Sources/Census-CD115-Gini-Index-17_5YR.csv", skip = 1) %>%
  rename(district = Geography, gini = `Estimate; Gini Index`, error = `Margin of Error; Gini Index`) %>%
  mutate(id1 = str_sub(Id2, start = 1, 2),
         id2 = str_sub(Id2, start = 3, 4)) %>%
  select(-Id, -Id2)

# data downloaded from https://cookpolitical.com/pvi-map-and-district-list
cooks_district <- read_csv("C:/Users/ignac/Desktop/RRepository/GunViolenceArchive/Data Sources/cooks_district.csv") %>%
  mutate(state_abbr = str_sub(Dist, 1, 2),
         id2 = str_sub(Dist, 4, 5)) %>%
  select(state_abbr, id2, Incumbent, PVI, `Clinton %`, `Trump %`) %>%
  bind_rows(tibble(state_abbr = "DC", id2 = "00", Incumbent = "Non-voting delegate", PVI = "D+43", `Clinton %` = 90.9, `Trump %` = 4.1)) %>% 
  mutate(party = ifelse(str_detect(PVI, pattern = "R"), "R", 
                 ifelse(str_detect(PVI, pattern = "D"), "D", "EVEN")),
         index = str_extract(PVI, "[0-9]+"),
         index = as.numeric(ifelse(is.na(index), 0, index)),
         index = ifelse(party == "R", -1*index, index),
         id2 = ifelse(str_detect(id2, "[A-Z]+"), "00", id2)) 

# district polygons
district_lines <- USAboundaries::us_congressional() %>%
  filter(jurisdiction_type != "territory") %>%
  select(statefp, cd115fp, state_name, state_abbr, geometry) %>%
  rename(id1 = statefp, id2 = cd115fp)

district_map <- district_lines %>%
  inner_join(Census_CD115_Gini_Index_17_5YR) %>%
  inner_join(cooks_district) %>%
  st_as_sf()

# Gun related incidents between 2016 - 2018
incidents <- readRDS("newdata2.rds")

incident_points <- map2(incidents$Longitude, incidents$Latitude, ~st_point(c(.x, .y))) %>%
  st_sfc(crs = 4326) %>%
  st_sf(incidents[, !(names(incidents) %in% c("Longitude", "Latitude"))], .)

incident_district_key <- bind_cols(incidents, district_map[as.numeric(st_within(incident_points, district_map)),]) %>%
  select(Incident, district, id1, id2)

district_summary <- incident_district_key %>%
  group_by(district) %>%
  count() %>%
  arrange((n))

district_map <- district_map %>%
  inner_join(district_summary)

district_info <- district_map %>%
  mutate(sq_miles = st_area(geometry),
         sq_miles = units::set_units(sq_miles, mi^2),
         sq_miles = as.numeric(sq_miles))

st_geometry(district_info) <- NULL  
options(scipen = 2)


```
<div class="gap">
</div>

<div class="jumbotron title">
<div class="container-fluid">
<div class="row">
<div class="col-lg-12 title-text">
<h1>Where is the gun violence coming from?</h1>
<h3>A partisan look into 115th Congressional Districts.</h3>
</div>
</div>
</div>
</div>

```{r echo=FALSE, message=FALSE, warning=FALSE}
#### SETTING COLORS

partisan_district_colors <- colorBin("RdBu", domain = c(-44, 44), bins = seq(-44, 44, length.out = 5))
gini_district_colors <- colorBin("Greens", domain = c(0.38, 0.6), bins = seq(0.38, .6, length.out = 5))
incident_district_colors <- colorBin("Oranges", domain = c(0, 2646), bins = seq(0, 2646, length.out = 5))

####

### SETTING LABELS

district_labels <- sprintf(
  "<strong>%s</strong>
  <br>Number of incidents: %g
  <br>Gini Index: %g
  <br>Partisan Index: %s",
  district_map$district, 
  district_map$n, 
  district_map$gini, 
  district_map$PVI
) %>% lapply(htmltools::HTML)

###
```
<div class="container-fluid map">
<div class="row">
<div class="col-lg-3 col-md-2 col-sm-1 col-xs-0"></div>
<div class="col-lg-6 col-md-8 col-sm-10 col-xs-12">
<h1 id="the-data"> the data </h1>
<ul>
<li><i class="fas fa-asterisk"></i>Gun related incidents were collected from [Gun Violence Archive](https://www.gunviolencearchive.org/).</li>
<li><i class="fas fa-asterisk"></i>Congressional district shape files were gathered from the **USAboundaries** packages in R. </li>
<li><i class="fas fa-asterisk"></i>The partisanship between congressional districts can be found from the [Cook Political Report](https://cookpolitical.com/pvi-map-and-district-list). </li>
<li><i class="fas fa-asterisk"></i>Income inequality can be found on the [United States Census](https://factfinder.census.gov/faces/tableservices/jsf/pages/productview.xhtml?pid=ACS_17_5YR_B19083&prodType=table)  website.</li>
</ul>
</div>
<div class="col-lg-3 col-md-2 col-sm-1 col-xs-0"></div>
</div>
<div class="row">
<div class="col-lg-3"></div>
<div class="col-lg-6">
<center>
<svg xmlns="http://www.w3.org/2000/svg" class="line-divider" width="100%" height="60" viewBox="0 0 400 26.1" style="max-width:80%" fill="url(#gradient-across);" aria-hidden="true" focusable="false"><g id="svgg"><path id="path0" d="M119.3 0.8C112.8 3.6 113.9 10.2 121.9 15.5 123.5 16.6 123.7 16.5 116.5 18.7 94.1 25.5 81.1 25.5 70.8 18.6 66 15.4 64.6 16.1 68.8 19.7 77.7 27.5 95.1 28.1 122.3 21.5L129 19.9 133 21.2C147.5 25.9 175.4 24 193.4 17.1 193.8 16.9 194.4 17.6 194.9 18.6 197.1 23.2 205.9 22.4 205.9 17.7 205.9 16.7 206.2 16.7 209.5 17.9 228.1 24.2 253.2 25.7 266.8 21.2L271 19.8 279 21.7C306.6 28.1 322.2 27.5 331.2 19.7 334.7 16.7 334 15.1 330.4 17.9 321.3 25.2 307.1 25.6 285.2 19.2L277.1 16.8 280.4 13.6C285.6 8.6 286.5 5.3 283.5 2.6 279.2-1.1 271.6-0.2 273.4 3.9 274 5.1 274.2 5.2 275.9 4.9 281 4 282 4 282.7 4.8 284.1 6.5 282.1 9.7 277.2 13.6L274.4 15.7 269.6 14.3C244.9 6.9 222 6 207.6 12 205.8 12.8 205.7 12.8 204.6 11.8 202.1 9.4 198.4 9.5 195.9 11.8 194.8 12.8 194.8 12.8 191.8 11.7 175.1 5.9 153.5 7 128.8 14.8L125.7 15.8 123.5 14.2C118.7 10.8 115.9 6.5 117.3 4.8 118 4 119.1 4 124 4.9 125.6 5.2 126 5.1 126.5 4.1 128.1 1.2 123.4-1 119.3 0.8M79.8 8.9C72.3 10 65.1 11.5 50.6 15.1 24.7 21.6 7.9 21.4 4.2 14.8 3.2 13.2 1.6 12.8 0.5 14.1 -0.6 15.5 0.3 16.4 4.4 18.2 18.1 24.2 31.1 23.8 57.1 16.5 85.4 8.5 106.2 8.4 114.8 16.2 115.3 16.7 115.9 16.9 116.1 16.7 117.2 15.7 109.6 11.4 104 9.7 99 8.3 87.1 7.9 79.8 8.9M299.1 9C292.2 10.4 282.5 15.3 283.9 16.7 284.1 16.9 284.7 16.7 285.2 16.2 293.1 9.1 313.5 8.5 337.3 14.9 341.5 16 347.9 17.7 351.6 18.7 368.8 23.2 383.8 23.2 394.1 18.8 396.4 17.8 398.6 16.9 399.1 16.7 400.2 16.3 400.3 14.7 399.2 13.6 398 12.4 397.2 12.6 395.8 14.9 391.6 21.5 374.9 21.5 348.3 14.8 323 8.5 309.4 6.9 299.1 9M181.6 11.3C185.7 11.9 193.7 13.8 194.2 14.3 194.8 14.8 172.4 20.3 165.7 21.3 154.7 22.9 140.5 22.1 133.9 19.5 132.4 18.8 132.5 18.8 137.5 17.3 158.5 11.2 169.9 9.6 181.6 11.3M238.8 11.5C244.4 12.4 246.5 12.9 258.8 16.2 268.3 18.9 268.3 18.9 262.6 20.4 250.5 23.6 238 22.8 217.7 17.7 212.8 16.5 208.1 15.3 207.3 15.2 205.1 14.6 205.6 14.1 209.3 13.1 218.6 10.7 229.6 10.1 238.8 11.5"/></g></svg>
</center>
</div>
<div class="col-lg-3"></div>
</div>

<div class="row map">
<div class="col-lg-1 col-md-0 col-sm-0 col-xs-0"></div>
<div class="col-lg-4 col-md-6 col-sm-12 col-xs-12 map-text">
<p class="space">
<p>
Congressional districts all have around 711,000 people. We could compare incidents between states, because gun laws are mostly a state matter, but examining congressional districts offer greater insight into the role of partisanship in this nation-wide issue.
</p>
<p>
These represent all police-recorded gun incidents from 2016-2018. Suicides are included, which make up a majority of the incidents. *Note:* suicides are included because in countries with guns, successful suicides are highly correlated with the availability of a firearm. 
</p>
<p>
The *Cook Index* measures how each district voted in the past two elections. How much does each district lean towards it political affiliation? The higher the index number, the greater the political leaning of the respective district. 
</p>
<p>
The *gini index* measures the concentration of wealth within a certain area. Is poverty the major factor in gun related incidents? It can be. Past studies and a preliminary look into the data show that areas in which the income distribution in similar, there are fewer crimes. This means that if everyone is within the same economic class, crime rates tend to drop. The gini index shows the *economic disparity*, so a higher index means that the poor will perceive themselves are poorer. Keep this in mind as we examine the data further. The higher the number, the greater the wealth is concentrated by fewer people.
</p>
</div>
<div class="col-lg-6 col-md-6 col-sm-12 col-xs-12 map-chunk">
<h3>115th Congress, 2016 - 2018</h3>
```{r leaflet_map, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width="100%", paged.print=FALSE}
leaflet(district_map) %>%
addProviderTiles(providers$Stamen.Toner, group = "Map") %>%
#addProviderTiles(providers$CartoDB.PositronOnlyLabels) %>%
addPolygons(fillColor = ~gini_district_colors(gini), 
weight = .1,
opacity = 1,
color = "black",
label = ~district_labels,
group = "Income Inequality Index") %>%
addPolygons(fillColor = ~partisan_district_colors(index), 
weight = .1,
opacity = 1,
color = "black",
label = ~district_labels,
group = "Partisan Voter Index") %>%
addPolygons(fillColor = ~incident_district_colors(n), 
weight = .1,
opacity = 1,
color = "black",
label = ~district_labels,
group = "Number of Incidents") %>%
addLegend("topleft", pal = gini_district_colors, values = ~gini, group = "Income Inequality Index") %>%
addLegend("topleft", pal = partisan_district_colors, values = ~PVI, group = "Partisan Voter Index") %>%
addLegend("topleft", pal = incident_district_colors, values = ~n, group = "Number of Incidents") %>%
addLayersControl(
overlayGroups = c("Income Inequality Index", "Partisan Voter Index", "Number of Incidents"),
options = layersControlOptions(collapse = FALSE)
) %>%
setView(lng = -97, lat = 38, zoom = 5) %>%
hideGroup("Income Inequality Index") %>%
hideGroup("Partisan Voter Index") %>%
hideGroup("Number of Incidents")

```
</div>
<div class="col-lg-1 col-md-0 col-sm-0 col-xs-0"></div>
</div>
</div>
</div>

<!-- Summaries -->

<div class="container-fluid summaries">
<div class="col-lg-12">
<h1> In Summary </h1>
<div class="well">
<div id="myCarousel" class="carousel slide" data-interval="20000" data-pause="hover" data-ride="carousel">
<!-- Indicators -->
<ol class="carousel-indicators">
<li data-target="#myCarousel" data-slide-to="0" class="active"></li>
<li data-target="#myCarousel" data-slide-to="1"></li>
<li data-target="#myCarousel" data-slide-to="2"></li>
</ol>
<!-- Carousel items -->
<div class="carousel-inner" role="listbox">
<div class="item active">
<div class="row">
<div class="col-md-4">
<div class="thumbnail">
<h3>Incidents within Districts</h3>
<p>The closer to the left, the fewer the number of incidents that occured. Success here is marked by having the highest bar on the far left. Here, we see that Republicans clearly win. There are more blue boxes towards the right, indicating that Democrats have the most dangerous districts.</p>
</div>
</div>
<div class="col-md-8">
```{r echo=FALSE, out.width=700}
plot1 <- ggplot(district_info, aes(x = n, color = party, fill = party)) + 
  geom_histogram(alpha = 0.2, position = "identity") +
  theme(legend.position = "top") +
  scale_color_manual(values = c("blue", "white", "red")) +
  scale_fill_manual(values = c("blue", "white", "red")) +
  labs(title="", x = "Incidents", y = "# of Districts") + 
  theme_classic()
  
plotly::ggplotly(plot1)

```
</div>
</div>
<!--/row-->
</div>
<!--/item-->
<div class="item">
<div class="row">
<div class="col-md-4">
<div class="thumbnail">
<h3>Gun Violence by Income Inequality</h3>
<p>The further towards the right marks a higher Gini index, indicating that these districts have the majority of their wealth concentrated in the between fewer people. The higher the dot is, the greater the number of incidents that occured. Again, we see fewer red dots on the higher end of the chart.</p>
</div>
</div>
<div class="col-md-8">
```{r echo=FALSE, out.width=700}
district_info %>%
  filter(sq_miles <= 13000) %>%
  plotly::plot_ly(x = ~gini, y = ~n, type = 'scatter', color = ~party, colors = c("blue", "black", "red"),
          text = ~paste("Square Miles: ", sq_miles, 
                        '<br># of Incidents: ', n,
                        '<br>Gini Index: ', gini,
                        '<br>PVI: ', PVI,
                        '<br>Clinton vs Trump: ', `Clinton %`, '% vs', `Trump %`, '%',
                        '<br>District ', district))
```
</div>
</div>
<!--/row-->
</div>
<!--/item-->
<div class="item">
<div class="row">
<div class="col-md-4"><div class="thumbnail">
<h3>Incidents by Square Area</h3>
<p>Pay close attention to the y-axis; the number of incidents for Democrats ends below 3000, while for Republicans it ends around 500. The further to the left, the smaller the square miles the district is, meaning there are more people in a small area. We see that the red dots extend further towards the right than the blue dots.</p>
</div>
</div>
<div class="col-md-8">
```{r echo=FALSE, out.width=700}
district_info %>%
  filter(sq_miles <= 13000) %>%
  transform(id = as.integer(factor(party))) %>%
  plotly::plot_ly(x = ~sq_miles, y = ~n, type = 'scatter', color = ~party, colors = c("blue", "black", "red"),
          text = ~paste("Square Miles: ", sq_miles, 
                        '<br># of Incidents: ', n,
                        '<br>Gini Index: ', gini,
                        '<br>PVI: ', PVI,
                        '<br>Clinton vs Trump: ', `Clinton..`, '% vs', `Trump..`, '%',
                        '<br>District ', district),
          yaxis = ~paste0("y", id)) %>%
            plotly::subplot(nrows = 2, shareX = T, titleY = T)
```
</div>
</div>
<!--/row-->
</div>
<!--/item-->
</div>
<!--/carousel-inner-->
<!-- Left and right controls-->
<a href="#myCarousel" class="carousel-control left" data-slide="prev" role="button">
<span class="glyphicon glyphicon-chevron-left" aria-hidden="true"></span>
<span class="sr-only">Previous</span>
</a>
<a href="#myCarousel" class="carousel-control right" data-slide="next" role="button">
<span class="glyphicon glyphicon-chevron-right" aria-hidden="true"></span>
<span class="sr-only">Next</span>
</a>
</div>
<!--/myCarousel2-->
</div>
<!--/well-->
</div>
</div>

<div class="container-fluid district-table">
<div class="row rheader">
<div class="col-lg-3 col-md-3 col-sm-3 col-xs-12">
<h1>District Table</h1>
</div>
<div class="col-lg-6 col-md-6 col-sm-6 col-xs-12">
<center>
<svg xmlns="http://www.w3.org/2000/svg" class="line-divider-2" width="80%" height="30" viewBox="0 0 400 26.1" style="max-width:80%" fill="url(#gradient-across-2);" aria-hidden="true" focusable="false"><g id="svgg"><path id="path0" d="M119.3 0.8C112.8 3.6 113.9 10.2 121.9 15.5 123.5 16.6 123.7 16.5 116.5 18.7 94.1 25.5 81.1 25.5 70.8 18.6 66 15.4 64.6 16.1 68.8 19.7 77.7 27.5 95.1 28.1 122.3 21.5L129 19.9 133 21.2C147.5 25.9 175.4 24 193.4 17.1 193.8 16.9 194.4 17.6 194.9 18.6 197.1 23.2 205.9 22.4 205.9 17.7 205.9 16.7 206.2 16.7 209.5 17.9 228.1 24.2 253.2 25.7 266.8 21.2L271 19.8 279 21.7C306.6 28.1 322.2 27.5 331.2 19.7 334.7 16.7 334 15.1 330.4 17.9 321.3 25.2 307.1 25.6 285.2 19.2L277.1 16.8 280.4 13.6C285.6 8.6 286.5 5.3 283.5 2.6 279.2-1.1 271.6-0.2 273.4 3.9 274 5.1 274.2 5.2 275.9 4.9 281 4 282 4 282.7 4.8 284.1 6.5 282.1 9.7 277.2 13.6L274.4 15.7 269.6 14.3C244.9 6.9 222 6 207.6 12 205.8 12.8 205.7 12.8 204.6 11.8 202.1 9.4 198.4 9.5 195.9 11.8 194.8 12.8 194.8 12.8 191.8 11.7 175.1 5.9 153.5 7 128.8 14.8L125.7 15.8 123.5 14.2C118.7 10.8 115.9 6.5 117.3 4.8 118 4 119.1 4 124 4.9 125.6 5.2 126 5.1 126.5 4.1 128.1 1.2 123.4-1 119.3 0.8M79.8 8.9C72.3 10 65.1 11.5 50.6 15.1 24.7 21.6 7.9 21.4 4.2 14.8 3.2 13.2 1.6 12.8 0.5 14.1 -0.6 15.5 0.3 16.4 4.4 18.2 18.1 24.2 31.1 23.8 57.1 16.5 85.4 8.5 106.2 8.4 114.8 16.2 115.3 16.7 115.9 16.9 116.1 16.7 117.2 15.7 109.6 11.4 104 9.7 99 8.3 87.1 7.9 79.8 8.9M299.1 9C292.2 10.4 282.5 15.3 283.9 16.7 284.1 16.9 284.7 16.7 285.2 16.2 293.1 9.1 313.5 8.5 337.3 14.9 341.5 16 347.9 17.7 351.6 18.7 368.8 23.2 383.8 23.2 394.1 18.8 396.4 17.8 398.6 16.9 399.1 16.7 400.2 16.3 400.3 14.7 399.2 13.6 398 12.4 397.2 12.6 395.8 14.9 391.6 21.5 374.9 21.5 348.3 14.8 323 8.5 309.4 6.9 299.1 9M181.6 11.3C185.7 11.9 193.7 13.8 194.2 14.3 194.8 14.8 172.4 20.3 165.7 21.3 154.7 22.9 140.5 22.1 133.9 19.5 132.4 18.8 132.5 18.8 137.5 17.3 158.5 11.2 169.9 9.6 181.6 11.3M238.8 11.5C244.4 12.4 246.5 12.9 258.8 16.2 268.3 18.9 268.3 18.9 262.6 20.4 250.5 23.6 238 22.8 217.7 17.7 212.8 16.5 208.1 15.3 207.3 15.2 205.1 14.6 205.6 14.1 209.3 13.1 218.6 10.7 229.6 10.1 238.8 11.5"/></g></svg>
</center>
</div>
<div class="col-lg-3 col-md-3" col-sm-3 col-xs-0></div>
</div>
<div class="row">
<div class="col-lg-12 col-md-12 col-sm-12 col-xs-12">
```{r district-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(formattable)
library(DT)

#data_table <- district_info %>%
#  mutate(PVI = ifelse(index > 0, color_bar("lightblue")(index), color_bar("red")(index)),
#         gini = color_bar("lightgreen")(gini),
#         n = color_bar("yellow")(n)) %>%
#  select(district, state_name, `Clinton %`, `Trump %`, gini, error, sq_miles, Incumbent, PVI, n)
#formattable(datatable(data_table, options= list(pageLength= 5, scrollX=T)))

as.datatable(district_info %>%
  mutate(PVI = ifelse(index > 0, color_bar("lightblue")(index), color_bar("red")(index)),
         gini = color_bar("lightgreen")(gini),
         n = color_bar("yellow")(n)) %>%
  select(district, state_name, `Clinton %`, `Trump %`, gini, error, sq_miles, Incumbent, PVI, n) %>%
  formattable())
```
</div>
</div>
<div class="row rheader">
<div class="col-lg-3 col-md-3 col-sm-0 col-xs-0"></div>
<div class="col-lg-6 col-md-6 col-sm-12 col-xs-12">
<center>
<svg xmlns="http://www.w3.org/2000/svg" class="line-divider-2" width="80%" height="30" viewBox="0 0 400 26.1" style="max-width:80%" fill="url(#gradient-across-2);" aria-hidden="true" focusable="false"><g id="svgg"><path id="path0" d="M119.3 0.8C112.8 3.6 113.9 10.2 121.9 15.5 123.5 16.6 123.7 16.5 116.5 18.7 94.1 25.5 81.1 25.5 70.8 18.6 66 15.4 64.6 16.1 68.8 19.7 77.7 27.5 95.1 28.1 122.3 21.5L129 19.9 133 21.2C147.5 25.9 175.4 24 193.4 17.1 193.8 16.9 194.4 17.6 194.9 18.6 197.1 23.2 205.9 22.4 205.9 17.7 205.9 16.7 206.2 16.7 209.5 17.9 228.1 24.2 253.2 25.7 266.8 21.2L271 19.8 279 21.7C306.6 28.1 322.2 27.5 331.2 19.7 334.7 16.7 334 15.1 330.4 17.9 321.3 25.2 307.1 25.6 285.2 19.2L277.1 16.8 280.4 13.6C285.6 8.6 286.5 5.3 283.5 2.6 279.2-1.1 271.6-0.2 273.4 3.9 274 5.1 274.2 5.2 275.9 4.9 281 4 282 4 282.7 4.8 284.1 6.5 282.1 9.7 277.2 13.6L274.4 15.7 269.6 14.3C244.9 6.9 222 6 207.6 12 205.8 12.8 205.7 12.8 204.6 11.8 202.1 9.4 198.4 9.5 195.9 11.8 194.8 12.8 194.8 12.8 191.8 11.7 175.1 5.9 153.5 7 128.8 14.8L125.7 15.8 123.5 14.2C118.7 10.8 115.9 6.5 117.3 4.8 118 4 119.1 4 124 4.9 125.6 5.2 126 5.1 126.5 4.1 128.1 1.2 123.4-1 119.3 0.8M79.8 8.9C72.3 10 65.1 11.5 50.6 15.1 24.7 21.6 7.9 21.4 4.2 14.8 3.2 13.2 1.6 12.8 0.5 14.1 -0.6 15.5 0.3 16.4 4.4 18.2 18.1 24.2 31.1 23.8 57.1 16.5 85.4 8.5 106.2 8.4 114.8 16.2 115.3 16.7 115.9 16.9 116.1 16.7 117.2 15.7 109.6 11.4 104 9.7 99 8.3 87.1 7.9 79.8 8.9M299.1 9C292.2 10.4 282.5 15.3 283.9 16.7 284.1 16.9 284.7 16.7 285.2 16.2 293.1 9.1 313.5 8.5 337.3 14.9 341.5 16 347.9 17.7 351.6 18.7 368.8 23.2 383.8 23.2 394.1 18.8 396.4 17.8 398.6 16.9 399.1 16.7 400.2 16.3 400.3 14.7 399.2 13.6 398 12.4 397.2 12.6 395.8 14.9 391.6 21.5 374.9 21.5 348.3 14.8 323 8.5 309.4 6.9 299.1 9M181.6 11.3C185.7 11.9 193.7 13.8 194.2 14.3 194.8 14.8 172.4 20.3 165.7 21.3 154.7 22.9 140.5 22.1 133.9 19.5 132.4 18.8 132.5 18.8 137.5 17.3 158.5 11.2 169.9 9.6 181.6 11.3M238.8 11.5C244.4 12.4 246.5 12.9 258.8 16.2 268.3 18.9 268.3 18.9 262.6 20.4 250.5 23.6 238 22.8 217.7 17.7 212.8 16.5 208.1 15.3 207.3 15.2 205.1 14.6 205.6 14.1 209.3 13.1 218.6 10.7 229.6 10.1 238.8 11.5"/></g></svg>
</center>
</div>
<div class="col-lg-3 col-md-3 col-sm-0 col-xs-0"></div>
</div>
</div>

